Leadership across cultures and contexts: an exploratory analysis

### 2020-04-17 leadership_across_cultures_contexts.Rmd
Added mosaic plot of subsistence X region
Fixed feature X subsistence models. Added a couple of plots.

@@

@@

>>>>

```{r subsisttree, fig.cap="Composition of the study source data, organized by mode of subsistence and culture. Size the rectangles, in descending order, is proportional to the number of text records per mode of subsistence, cultures of each mode, and per document from each culture."}
plot_cult_docs_subsis
```

@@

## Continental region is confounded with mode of subsistence

```{r regionsubsistence, fig.cap=""}
ggplot(all_data2b) + geom_mosaic(aes(x = product(subsistence, region), fill = subsistence)) + scale_fill_viridis(discrete = T) + theme_minimal(15)
```

## Bias

@@

### Correlation matrix of features

```{r featurecor, fig.cap="Correlation matrix of Feature variables. Numbers and colors indicate Pearson correlation coefficients."}
plot_features_cor
```
